---
title: "Definition of the date period to download"
author: "Stijn Van Hoey"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{date_definition}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
library(dplyr)
library(ggplot2)
```

## Introduction

When downloading time series with the `get_timeseries_tsid()` method, the `ts_id` argument provides the link with the variable, location and frequency of the time series, but not the extent/period to download.

The time period to download is defined by a combination of the arguments `from`, `to` and `period`. The usage is similar with the [VMM documentation](https://www.waterinfo.be/download/9f5ee0c9-dafa-46de-958b-7cac46eb8c23?dl=0) for the API itself. The main difference is that the `wateRinfo` package uses existing R functions to interpret the date strings given by the user before sending these to the API (as a formatted string according to `%Y-%m-%d %H:%M:%S`).

This vignette aims to briefly explain how to define the arguments. 

## Which combinations?

In order to define a period, a start and end date is required. Defining all three will result in an error, but any combination of `from/to`, `from/period` and `to/period` is allowed. Moreover, if only `period` or `from` are defined, the waterinfo.be API will automatically define `to` as the current time. Hence, defining *the last x days/months/years/...* can be achieved by only using the `period` option.

## How to define the from/to dates

The package will both except valid date strings as well as valid date objects (`POSIXct`, `POSIXt`) as input for the `from` and `to` arguments. When using a string value, it can be defined on different resolutions:

* "2017-01-01 11:00:00"
* "2017-01-01"
* "2017-01"
* "2017"

According to the [`lubridate`](https://lubridate.tidyverse.org/) package, these orders are accepted: `ymd_hms`, `ymd`, `ym`, `y`. As a result, also `"2017/01/01"`, `"2017 01 01"` or `"20170101"` are valid date string inputs. Make sure the order of year-month-day is respected. For example, `"01/01/2017"`, `"01-01-2017"` and `"01-2017"` are NOT valid. 

## How to define the period

The period string provides a flexible way to extract a time period starting (in combination with `from`) or ending (in combination with `to`) at a given moment. Moreover, by using only the `period` as argument, it will cover all cases where one is interested in *the last x days/months/years/...*.

Some examples are:

* `P3D` : period of three days
* `P2Y` : period of 2 years
* `PT6H` : period of 6 hours
* `P2DT6H` : period of 2 days and 6 hours
* ...

In general, the period string should be provided as `P#Y#M#DT#H#M#S`, where P defines `Period` (always required!) and each # is an integer value expressing *the number of...*. The codes define a specific time interval:

* `Y` - years
* `M` - months
* `D` - days
* `W` - weeks
* `H` - hours
* `M` - minutes
* `S` - seconds

`T` is required if codes about sub-day resolution (day, minutes, hours) is part of the period string. Furthermore, `D` and `W` are mutually exclusive.

More examples of valid period strings are:

* `P1DT12H` : period of 1 day and 12 hours
* `P2WT12H` : period of 2 weeks and 12 hours
* `P1Y6M3DT4H20M30S`: period of 1 year, six months, 3 days, 4 hours, 20 minutes and 30 seconds

## Examples

```{r loadlibrary, warning = FALSE}
library(wateRinfo)
```

When interested in irradiance (15min frequency) data, the following stations provide time series:

```{r irr_stats}
get_stations("irradiance")
```

Focusing on the data of Herentals, the `ts_id` to use is `78930042`. We have different options to define the period to get data from:

1. data about **the last day**, using `period` only:

```{r lastday, fig.width = 7}
irr_lastday <- get_timeseries_tsid("78930042", period = "P1D")
ggplot(irr_lastday, aes(Timestamp, Value)) +
    geom_line() + xlab("") + ylab("irradiance (W/m2)")
```

2. data about **the last 12 hours, 30 minutes**, using `period` only:

```{r lasthours, fig.width = 7}
irr_lasthours <- get_timeseries_tsid("78930042", period = "PT12H30M")
ggplot(irr_lasthours, aes(Timestamp, Value)) +
    geom_line() + xlab("") + ylab("irradiance (W/m2)")
```

3. historical data **from July till August 2014**, using `from` and `to` on month level

```{r historic, fig.width = 7}
irr_2014 <- get_timeseries_tsid("78930042", 
                                from = "2014-07-01", 
                                to = "2014-08-01")
ggplot(irr_2014, aes(Timestamp, Value)) +
    geom_line() + xlab("") + ylab("irradiance (W/m2)")
```

4. historical data for **one day from July 1st 2014**, using `from` and `period`

```{r day2014, fig.width = 7}
irr_2014day <- get_timeseries_tsid("78930042", 
                                from = "2014-07-01", 
                                period = "P1D")
ggplot(irr_2014day, aes(Timestamp, Value)) +
    geom_line() + xlab("") + ylab("irradiance (W/m2)")
```
