---
title: "Download time series from Waterinfo.be"
author: "Stijn Van Hoey"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{downloading}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Introduction

The [waterinfo.be](https://www.waterinfo.be) API uses a system of identifiers, called `ts_id` to define individual time series. For example, the identifier `ts_id` = `78073042` corresponds to the time series of air pressure data for the measurement station in Liedekerke, with a 15 min time resolution. Hence, the `ts_id` identifier defines a variable of interest from a measurement station of interest with a specific frequency (e.g. 15 min, hourly,...). The knowledge of the proper identifier is essential to be able to download the corresponding data.

```{r}
library(wateRinfo)
library(dplyr)
```


# Downloading with known identifier

In case you already know the `ts_id` identifier that defines your time serie, the package provides the function `get_timeseries_tsid` to download a specific period of the time series. 

As an example, to download the air pressure data of Liedekerke for the first of January 2016:

```{r tsdownload}
my_data <- get_timeseries_tsid("78073042", from = "2016-01-01", to = "2016-01-02")
knitr::kable(head(my_data), align = "lcc")
```

For more information on the possibilities in defining the period of the download, a separate vignette is available. Let's have a visual check of our downloaded data, using the `ggplot2` package:

```{r}
library(ggplot2)
my_data %>% 
    ggplot(aes(Timestamp, Value)) + 
    geom_line()
```


# Search identifier based on station name



# Search identifier based on variable name



# Downloading time series in batch 

## Download all stations for a given variable

```{r station_of_var, eval = FALSE}
# http://r-pkgs.had.co.nz/vignettes.html - options vignette
# extract the available stations for a predefined variable
variable_of_interest <- "luchtdruk"
stations <- get_stations(variable_of_interest)

# Download the data for a given period for each of the stations
station_data <- stations %>%
    group_by(ts_id) %>%
    do(get_timeseries_tsid(.$ts_id, period = "P1D")) %>%
    ungroup() %>%
    left_join(stations, by = "ts_id")

# create a plot of the individua datasets
station_data %>% 
    ggplot(aes(x = Timestamp, y = Value)) + 
    geom_point() + 
    facet_wrap(c("station_name", "stationparameter_name"))
```

## Download set of variables from a station

```{r var_of_station, eval = FALSE}
station_of_interest <- "ME07_006"
variables <- get_variables(station_of_interest)

variables_to_download <- variables %>% 
    filter(parametertype_name == "Bodemvocht") %>%
    filter(ts_name == "P.15")

variables_updated <- variables_to_download %>%
    group_by(ts_id) %>%
    do(get_timeseries_tsid(.$ts_id, period = "P1D")) %>%
    ungroup() %>%
    left_join(variables, by = "ts_id")

variables_updated %>% 
    ggplot(aes(x = Timestamp, y = Value)) + 
    geom_point() + 
    facet_wrap(c("ts_name", "stationparameter_name"), scales = "free")
```

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
