---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Download all stations for a given variable

```{r station_of_var}
# extract the available stations for a predefined variable
variable_of_interest <- "luchtdruk"
stations <- get_stations(variable_of_interest)

# Download the data for a given period for each of the stations
station_data <- stations %>%
    group_by(ts_id) %>%
    do(get_timeseries_tsid(.$ts_id, period = "P1D")) %>%
    ungroup() %>%
    left_join(stations, by = "ts_id")

# create a plot of the individua datasets
station_data %>% 
    ggplot(aes(x = Timestamp, y = Value)) + 
    geom_point() + 
    facet_wrap(c("station_name", "stationparameter_name"))
```

## Download set of variables from a station

```{r var_of_station}
station_of_interest <- "ME07_006"
variables <- get_variables(station_of_interest)

variables_to_download <- variables %>% 
    filter(parametertype_name == "Bodemvocht") %>%
    filter(ts_name == "P.15")

variables_updated <- variables_to_download %>%
    group_by(ts_id) %>%
    do(get_timeseries_tsid(.$ts_id, period = "P1D")) %>%
    ungroup() %>%
    left_join(variables, by = "ts_id")

variables_updated %>% 
    ggplot(aes(x = Timestamp, y = Value)) + 
    geom_point() + 
    facet_wrap(c("ts_name", "stationparameter_name"), scales = "free")
```


## intro

Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
